Value Ordering, Discrepancies, and Restarts in Subgraph Solvers: \\ Some Half-Baked Mucking Around

### 2017-09-27 paper/paper.tex
Cite

?? Other studies use a random selection of 200 of each of the mesh and images instances, partly
because some earlier solvers find many of these instances extremely hard, and partly to avoid
skewing a portfolio. We want larger numbers of satisfiable instances, so we include all pattern /
target pairs. This gives a total of 14,621 instances, ?? of which we know are satisfiable, and ??
unsatisfiable.

>>>>

?? Other studies use a random selection of 200 of each of the mesh and images instances
\citep{DBLP:journals/cviu/DamiandSHJS11}, partly because some earlier solvers find many of these
instances extremely hard, and partly to avoid skewing a portfolio. We want larger numbers of
satisfiable instances, so we include all pattern / target pairs. This gives a total of 14,621
instances, ?? of which we know are satisfiable, and ??  unsatisfiable.
